File\+: \hyperlink{_t_m_8h}{T\+M.\+h} Author\+: Zoltan Fuzesi C00197361, IT Carlow, Software Engineering,

Supervisor \+: Joe Kehoe,

C++ Software Transactional Memory,

Created on December 18, 2017, 2\+:09 PM Transaction Manager class fields and methods declarations\hypertarget{index_OSTM}{}\subsection{Object Based Software Transactional Memory.}\label{index_OSTM}
\hyperlink{class_o_s_t_m}{O\+S\+TM} is a polymorphic solution to store and manage shared memory spaces within c++ programming context.~\newline
 You can store and managed any kind of object in transactional environment as a shared and protected memory space, if your class inherited from the \hyperlink{class_o_s_t_m}{O\+S\+TM} base class, and follows the required steps.\hypertarget{index_install_sec}{}\subsubsection{Brief. Download the zip file from the provided (\+Windows, Linux, M\+A\+C O\+S\+X)link in the web-\/site,}\label{index_install_sec}
that contains the libostm.\+so, \hyperlink{_t_m_8h}{T\+M.\+h}, \hyperlink{_t_x_8h}{T\+X.\+h}, \hyperlink{_o_s_t_m_8h}{O\+S\+T\+M.\+h} files.\+Unzip the archive file to the desired destination possibly where you program is stored. Copy the library (Shared, Static) to the destination directory. Implement the inheritance from the base class. Create an executable, and run the application.\hypertarget{index_step1}{}\subsubsection{Step 1\+: Download the archive file.}\label{index_step1}
\hypertarget{index_step2}{}\subsubsection{Step 2\+: Unzip in to the target destination.}\label{index_step2}
\hypertarget{index_step3}{}\subsubsection{Step 3\+: Copy the shared library (libostm.\+so) to the operating system folder where the other shared library are stored.}\label{index_step3}
It will be different destination folder on different platforms. (Linux, Windows, Mac OS) \href{http://serversite.info/ostm/#tutorial}{\tt More Information}\hypertarget{index_step4}{}\subsubsection{Step 4\+: Achieve the required class hierarchy between the O\+S\+T\+M library and your own class structure.}\label{index_step4}
Details and instruction of class hierarchy requirements can be found on the web-\/site. www.\+serversite.\+info/ostm\hypertarget{index_step5}{}\subsubsection{Step 5\+: Create an executable file as you linking together the library, the $\ast$.\+h files with your own files.}\label{index_step5}
\hypertarget{index_step6}{}\subsubsection{Step 6\+: Now your application use transactional environment, that guarantees the consistency between object transactions.}\label{index_step6}
\hypertarget{index_step7}{}\subsubsection{Step 7\+: Run the application.}\label{index_step7}
